Water discharge has a variable impact on sediment transport capacity in subglacial systems

### 2023-08-25 Delaneyetal2023b.tex
more small changes

\begin{figure}[h]
  \centering
    \includegraphics[width=0.9\linewidth]{Fig4.png}
    \caption{Variance (measured by the standard deviation) in water velocity, shear stress, and total shear stress for different time aggregations across the range of subglacial and subaerial channel shapes and friction factors. 
    %The subglacial (blue) and subaerial (orange) systems are distinguished as are \alpine{} (a-c) and \icesheet{} (d-f).
      Shaded areas denote the $5^{\mathrm{th}}$ and $95^{\mathrm{th}}$ quantiles of the $100$ parameter combinations tested for each of the systems (Section~\ref{sect:imp}).
      Solid lines denote  mean values.
      Time intervals shown with markers denote $15$\,\unit{min}, $1$\,\unit{hr}, $12$\,\unit{hr}, $1$\,\unit{d}, $5$\,\unit{d}, $10$\,\unit{d}, and $15$\,\unit{d} aggregation periods.
      Text in columns shows rank correlation between the variable and sediment discharge for the corresponding time period for the subglacial (right column) and subaerial (left column) channels.
      } 
    \label{fig:multi_run}
  \end{figure}

@@

Over time scales longer than days to weeks, the glacier's sediment transport capacity reacts to the ice thickness, controlling the channel closure rate, and the surface slope of the glacier \citep[Figure~\ref{fig:multi_run}, ~ Section~\ref{sect:sub_mode}; ][]{rothlisberger1972,shreve1972,stevens2022}.
If the glacier is in a supply-limited state, often assumed in landscape evolution models, then the sediment discharge record also represents additional processes of sediment availability and bedrock erosion from  water pressure variations and sliding  \citep[e.g.][]{iverson2012,herman2015,delaney2023}.
This multitude of processes lies in contrast to most subaerial systems, where transport capacity typically increases with water discharge and hydraulic gradient, and the hydraulic gradient generally remains stable over time scales ranging from years to millennia \citep[Section~\ref{sect:fluv}; e.g.][]{muller1968,whipple1999,wickert2019}.
The stronger link between sediment export and hydrological forcing in subaerial channels means that variations in sediment transport records can be more easily attributed to climatic conditions than in  subglacial systems

>>>>

\begin{figure}[h]
  \centering
    \includegraphics[width=0.9\linewidth]{Fig4.png}
    \caption{Variance (measured by the standard deviation) in water velocity, shear stress, and total shear stress for different time aggregations across the range of subglacial and subaerial channel shapes and friction factors. 
      Shaded areas denote the minimum and maximum of the $100$ parameter combinations tested for each of the systems (Section~\ref{sect:imp}).
      Solid lines denote  mean values.
      Time intervals shown with markers denote $15$\,\unit{min}, $1$\,\unit{hr}, $12$\,\unit{hr}, $1$\,\unit{d}, $5$\,\unit{d}, $10$\,\unit{d}, and $15$\,\unit{d} aggregation periods.
      Text in columns shows rank correlation between the variable and sediment discharge for the corresponding time period for the subglacial (right column) and subaerial (left column) channels.
      } 
    \label{fig:multi_run}
  \end{figure}

@@

Over time scales longer than days to weeks, the glacier's sediment transport capacity reacts to the ice thickness, controlling the channel closure rate, and the surface slope of the glacier \citep[Figure~\ref{fig:multi_run}, ~ Section~\ref{sect:sub_mode}; ][]{rothlisberger1972,shreve1972,stevens2022}.
If the glacier is in a supply-limited state, often assumed in landscape evolution models, then the sediment discharge record also represents additional processes of sediment availability and bedrock erosion from  water pressure variations and sliding  \citep[e.g.][]{iverson2012,herman2015,delaney2023}.
This multitude of processes lies in contrast to most subaerial systems, where transport capacity typically increases with water discharge and hydraulic gradient, and the hydraulic gradient generally remains stable over time scales ranging from years to millennia \citep[Section~\ref{sect:fluv}; e.g.][]{muller1968,whipple1999,wickert2019}.
The stronger link between sediment transport capacity and hydrological forcing in subaerial channels means that variations in sediment transport records can be more easily attributed to climatic conditions than in  subglacial systems.
